---
title: "Homework Five Submission 1"
author: "Safia Read"
format:
  pdf:
    output-file: "read-s-hwk5-1"
    output-ext:  "pdf"
    header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
---

Github Link: https://github.com/safiaread/homework_5

```{r, echo = F, warning = F, message = F}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, scales, acs, tidyr)
data <- read.delim("/Users/safiaread/Desktop/homework_5/data/output/acs_medicaid.txt")
```

Question 1
```{r, echo = F, warning = F, message = F}
data%>%
group_by(year)%>%
summarise(adult_share = sum(ins_direct)/sum(adult_pop))%>%
ggplot(aes(y = adult_share, x = year))+
geom_line()
```

Question 2

The success of the program may have been affected by Trump-era policies since the reduction begins in 2016.

Question 3
```{r, echo = F, warning = F, message = F}
data%>%
group_by(year)%>%
summarise(adult_share = sum(ins_medicaid)/sum(adult_pop))%>%
ggplot(aes(y = adult_share, x = year))+
geom_line()
```

Question 4
```{r, echo = F, warning = F, message = F}
data <- data%>%
mutate(expand_14 = ifelse(expand_year != "2014" | is.na(expand_year), FALSE, TRUE))

data%>%
filter(is.na(expand_year)| expand_14 == TRUE)%>%
group_by(year, expand_14)%>%
summarise(adult_share = sum(uninsured)/sum(adult_pop))%>%
ggplot(aes(y = adult_share, x = year, color = expand_14))+
geom_line()
```

Question 5
```{r, echo = F, warning = F, message = F}
data <- data%>%
mutate(expand_14 = ifelse(expand_year != "2014" | is.na(expand_year), "not expanded", "expanded"))

data%>%
filter(year == "2012" | year == "2015")%>%
group_by(year, expand_14)%>%
summarise(percent_uninsured = mean(uninsured/adult_pop, na.rm = T))%>%
pivot_wider(names_from = expand_14, values_from = percent_uninsured)
```

Question 6
```{r, echo = F, warning = F, message = F}
library(modelsummary)

reg.data <- data %>% filter(expand_year==2014 | is.na(expand_year), !is.na(expand_ever)) %>%
  mutate(perc_unins=uninsured/adult_pop,
         post = (year>=2014), 
         treat=post*expand_ever)

#summary(lm(perc_unins ~ post + expand_ever + post*expand_ever, data=reg.data))
dd.ins.reg <- lm(perc_unins ~ post + expand_ever + post*expand_ever, data=reg.data)
modelsummary(list("DD (2014)"=dd.ins.reg),
             shape=term + statistic ~ model, 
             gof_map=NA,
             coef_omit='Intercept',
             vcov=~State
         )
```

Question 7
```{r, echo = F, warning = F, message = F}
library(fixest)

m.dd <- lm(perc_unins ~ post + expand_ever + treat, data=reg.data)

m.twfe <- feols(perc_unins ~ treat | State + year, data=reg.data)

msummary(list("DD"=m.dd, "TWFE"=m.twfe),
         shape=term + statistic ~ model, 
         gof_map=NA,
         coef_omit='Intercept',
         vcov=~State
         )
```

Question 8

Yes, the regression is different. This would make sense as the effect for states that adopted the expansion later will probably be different than those that adopted in 2014.
```{r, echo = F, warning = F, message = F}
reg.data <- data %>% filter(!is.na(expand_ever)) %>%
  mutate(perc_unins=uninsured/adult_pop,
         post = (year>=2014), 
         treat=post*expand_ever)

m.dd <- lm(perc_unins ~ post + expand_ever + treat, data=reg.data)
m.twfe <- feols(perc_unins ~ treat | State + year, data=reg.data)

msummary(list("DD"=m.dd, "TWFE"=m.twfe),
         shape=term + statistic ~ model, 
         gof_map=NA,
         coef_omit='Intercept',
         vcov=~State
         )
```

Question 9
```{r, echo = F, warning = F, message = F}
reg.dat <- data %>% 
  filter(expand_year==2014 | is.na(expand_year), !is.na(expand_ever)) %>%
  mutate(perc_unins=uninsured/adult_pop,
         post = (year>=2014), 
         treat=post*expand_ever)

mod.twfe <- feols(perc_unins~i(year, expand_ever, ref=2013) | State + year,
                  cluster=~State,
                  data=reg.dat)

iplot(mod.twfe, 
      xlab = 'Time to treatment',
      main = 'Event study')

```

Question 10
```{r, echo = F, warning = F, message = F}
reg.dat <- data %>% 
  filter(!is.na(expand_ever)) %>%
  mutate(perc_unins=uninsured/adult_pop,
         post = (year>=2014), 
         treat=post*expand_ever,
         time_to_treat = ifelse(expand_ever==FALSE, 0, year-expand_year),
         time_to_treat = ifelse(time_to_treat < -3, -3, time_to_treat))

mod.twfe <- feols(perc_unins~i(time_to_treat, expand_ever, ref=-1) | State + year,
                  cluster=~State,
                  data=reg.dat)

iplot(mod.twfe, 
      xlab = 'Time to treatment',
      main = 'Event study')
```